Identification of protoneutron star g-modes in gravitational-wave data \pcd{[PCD: alt. title]Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.}

### 2020-09-15 simulations.tex
New sentence in section II

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the AENUS-ALCAR code
(see Table~\ref{Tab:2dSimList} for a list of models).
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the EOS of
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
(GShen) for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.

>>>>

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the AENUS-ALCAR code
(see Table~\ref{Tab:2dSimList} for a list of models).
\pcd{Unlike the model set, the simulations in the test set cannot be 1D becase we need to extract the gravitational wave signal, which is
a multi-dimensional effect.. }
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the EOS of
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
(GShen) for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.
